Analyses

### 2022-09-09 report/online-appendix.Rmd
final version

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, warning=FALSE)
options(kableExtra.latex.load_packages = FALSE)
options(tinytex.verbose = TRUE)
options(scipen = 1, digits = 2)
# Uncomment below if you want code captions
# oldSource <- knitr::knit_hooks$get("source")
# knitr::knit_hooks$set(source = function(x, options) {
#   x <- oldSource(x, options)
#   x <- ifelse(!is.null(options$code.cap), paste0(x, "\\captionof{chunk}{", options$code.cap,"}"), x)
#   ifelse(!is.null(options$ref), paste0(x, "\\label{", options$ref,"}"), x)
# })
# Add `chunkcaption: TRUE` to YAML as well.
```

@@

\newpage
# Pre-Registered and Explorative Analysis
Table \ref{tab:h1} demonstrates the results as visualized in Figure 1 in the paper.
```{r "h1", fig.align="center", fig.height=5, fig.width=6}
p1 <- d %>% 
  mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
  select(POST_2, POST_3, ethnic) %>%
  pivot_longer(cols = POST_2:POST_3) %>%
  group_by(ethnic, name) %>%
  summarise(value = list(value)) %>%
  spread(ethnic, value) %>%
  group_by(name) %>%
  mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
         t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
         means_civic = t.test(unlist(`Civic Conception`))$estimate,
         means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
         means_difference = means_civic - means_ethnic,
         lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
         name = recode(name,
                       `POST_2` = "DV: People, not politicians, should make the most  important political decisions",
                       `POST_3` = "DV: MPs should follow the will of the people")) %>%
  select(var = name, p_value, t_value, means_difference, lower, higher) %>%
  pivot_longer(cols = p_value:higher) %>%
  mutate(name = recode(name,
                       `p_value` = "p-value",
                       `t_value` = "t-value",
                       `means_difference` = "Differences in Means",
                       `lower` = "CI: Lower Bound",
                       `higher` = "CI: Upper Bound")) %>%
  ungroup()

@@

kbl(p1, booktabs =T, caption = "\\label{tab:h1}Table Results H1") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm")  %>%
  column_spec(3, width = "4cm")

```
\newpage

Table \ref{tab:h2a} and \ref{tab:h2b} demonstrate the results as visualized in Figure 2 in the paper.
```{r "h2a", fig.align="center", fig.height=5, fig.width=6}
df <- d %>%
  mutate(a = HT4)
h2a <- regression2(df, a, ethnic) %>%
  pivot_longer(cols = AME) %>%
  mutate(a = recode(a, 
                    `1` = "1 (Low)", `2` = "2", `3` = "3", `4` = "4",
                    `5` = "5 (High"),
         y = recode(y,
                    `POST_2` = "DV: People, not politicians, should make the most  important political decisions",
                    `POST_3` = "DV: MPs should follow the will of the people")) %>%
  select(`Dependent Variable` = y, `Levels of National Exclusivity` = a,
         AME = value, `CI: Lower Bound` = lower, `CI: Upper Bound` = upper)

kbl(h2a, booktabs =T, caption = "\\label{tab:h2a}Table Results H2a") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")
```

@@

@@

```{r oa-cfa2, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:cfa}CFA Distribution"}
knitr::include_graphics(here::here("report/figures", "scale-1.png"))
```
## Additive scale
```{r "oa-addative", fig.align="center", fig.height=8, fig.width=12}
source(here("src/analysis/additive-scale.R"))

@@

## Wüttke et al. Approach
```{r "oa-wuttke", fig.align="center", fig.height=8, fig.width=12}
source(here("src/analysis/wuttke-approach.R"))

@@

## IRT Analyse
```{r "oa-irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide',message=FALSE,warning=FALSE}
source(here("src/analysis/IRT.R"))
```
```{r oa-irt1, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:irt1}IRT Distribution (1)"}
knitr::include_graphics(here::here("report/figures", "irt-1.png"))
```

@@

>>>>

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE,
                      message=FALSE, warning=FALSE)
options(kableExtra.latex.load_packages = FALSE)
options(tinytex.verbose = TRUE)
options(scipen = 1, digits = 2)
knitr::opts_chunk$set(fig.pos = "h", out.extra = "")
# Uncomment below if you want code captions
# oldSource <- knitr::knit_hooks$get("source")
# knitr::knit_hooks$set(source = function(x, options) {
#   x <- oldSource(x, options)
#   x <- ifelse(!is.null(options$code.cap), paste0(x, "\\captionof{chunk}{", options$code.cap,"}"), x)
#   ifelse(!is.null(options$ref), paste0(x, "\\label{", options$ref,"}"), x)
# })
# Add `chunkcaption: TRUE` to YAML as well.
```

@@

\newpage
# Pre-Registered and Explorative Analysis
## Differences in Ethnic and Civic Conceptions of the People
Table \ref{tab:h1} demonstrates the results as visualized in Figure 1 in the paper.

```{r "h1", fig.align="center", fig.height=5, fig.width=6}
p1 <- d %>% 
  mutate(ethnic = recode(ethnic, `1` = "Ethnic Conception",  `0` = "Civic Conception")) %>%
  select(POST_2, POST_3, ethnic) %>%
  pivot_longer(cols = POST_2:POST_3) %>%
  group_by(ethnic, name) %>%
  summarise(value = list(value)) %>%
  spread(ethnic, value) %>%
  group_by(name) %>%
  mutate(p_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$p.value,
         t_value = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$statistic,
         means_civic = t.test(unlist(`Civic Conception`))$estimate,
         means_ethnic = t.test(unlist(`Ethnic Conception`))$estimate,
         means_difference = means_civic - means_ethnic,
         lower = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[1],
         higher = t.test(unlist(`Civic Conception`), unlist(`Ethnic Conception`))$conf.int[2],
         name = recode(name,
                       `POST_2` = "DV: People, not politicians, should make the most important political decisions",
                       `POST_3` = "DV: MPs should follow the will of the people")) %>%
  select(var = name, p_value, t_value, means_difference, lower, higher) %>%
  pivot_longer(cols = p_value:higher) %>%
  mutate(name = recode(name,
                       `p_value` = "p-value",
                       `t_value` = "t-value",
                       `means_difference` = "Differences in Means",
                       `lower` = "CI: Lower Bound",
                       `higher` = "CI: Upper Bound")) %>%
  ungroup()

@@

kbl(p1, booktabs =T, caption = "\\label{tab:h1}Differences in Ethnic and Civic Conceptions of the People") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "4cm") %>%
  column_spec(2, width = "4cm")  %>%
  column_spec(3, width = "4cm")
```
\newpage

## Average Marginal Effects for Ethnic Conception of the People
Table \ref{tab:h2a} and \ref{tab:h2b} demonstrate the results as visualized in Figure 2 in the paper.
```{r "h2a", fig.align="center", fig.height=5, fig.width=6}
df <- d %>%
  mutate(a = HT4)
h2a <- regression2(df, a, ethnic) %>%
  pivot_longer(cols = AME) %>%
  mutate(a = recode(a, 
                    `1` = "1 (Low)", `2` = "2", `3` = "3", `4` = "4",
                    `5` = "5 (High"),
         y = recode(y,
                    `POST_2` = "DV: People, not politicians, should make the most  important political decisions",
                    `POST_3` = "DV: MPs should follow the will of the people")) %>%
  select(`Dependent Variable` = y, `Levels of National Exclusivity` = a,
         AME = value, `CI: Lower Bound` = lower, `CI: Upper Bound` = upper)

kbl(h2a, booktabs =T, caption = "\\label{tab:h2a}Average Marginal Effects for Ethnic Conception of the People") %>%
  kable_styling(latex_options = c("striped", "hold_position"),
                full_width = F, fixed_thead = T, position = "center") %>%
  column_spec(1, width = "5cm") %>%
  column_spec(2, width = "3cm") %>%
  column_spec(3, width = "2cm") %>%
  column_spec(4, width = "2cm") %>%
  column_spec(5, width = "2cm")
```

@@

## Exploration with Age, Region, Ideoligy and Attitude towards Political Pluralism
```{r results-explor, out.width = "100%", fig.align = 'center', fig.cap = "\\label{fig:results-h2}Average Marginal Effects for Ethnic Conception of the People"}
knitr::include_graphics(here("report/figures", "explorative-2.png"))
```

@@

```{r oa-cfa2, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:cfa}CFA Distribution"}
knitr::include_graphics(here::here("report/figures", "scale-1.png"))
```

\newpage
## Additive scale
```{r "oa-addative", fig.align="center", fig.height=8, fig.width=12}
source(here("src/analysis/additive-scale.R"))

@@

\newpage
## Wüttke et al. Approach
```{r "oa-wuttke", fig.align="center", fig.height=8, fig.width=12}
source(here("src/analysis/wuttke-approach.R"))

@@

\newpage
## IRT Analyse
```{r "oa-irt-code", fig.align="center", fig.height=8, fig.width=12, results="hide", fig.show='hide',message=FALSE,warning=FALSE}
source(here("src/analysis/IRT.R"))
```
```{r oa-irt1, out.width = "60%", fig.align = 'center', fig.cap = "\\label{fig:irt1}IRT Distribution (1)"}
knitr::include_graphics(here::here("report/figures", "irt-1.png"))
```

@@

\newpage
# References

### 2022-09-09 src/analysis/analyses.Rmd
final version

#(pe2 + pe3)/ (pe4 + pe5)
```

```{r "h1-extra", fig.align="center", fig.height=6, fig.width=12, echo = FALSE, fig.show = "hide"}
p1 + pe2 + 
  plot_layout(widths = c(1, 1.25))
```

>>>>

(pe2 + pe3)/ (pe4 + pe5)
```

```{r "h1-extra", fig.align="center", fig.height=6, fig.width=12, echo = FALSE, fig.show = "hide", eval = FALSE}
p1 + pe2 + 
  plot_layout(widths = c(1, 1.25))
```
